Recruiting Chapter

### 2021-05-17 text/tables_figures_may_2021.Rmd
draft changes

```{r event-count-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for public institutions"}
knitr::include_graphics('./../assets/figures/plot_event_count_pubu.pdf')
```

```{r event-count-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for private institutions"}
knitr::include_graphics('./../assets/figures/plot_event_count_privu.pdf')
```

@@

```{r, include = FALSE}
# ggplot's default color palette
# library(scales)
# show_col(hue_pal()(4))

@@

@@

```{r ego-network-figure-region, eval = FALSE, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of visited private HS, region"}
knitr::include_graphics('./../assets/figures/ego_network_figure_region.pdf')
```

@@

```{r hs-print-privu, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_privu.RDS') %>% head(n=20)

@@

```{r hs-table-privu-agg, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_agg_privu.RDS')

@@

```{r hs-print-pubu, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_pubu.RDS') %>% head(n=20)

@@

```{r hs-table-pubu-agg, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_agg_pubu.RDS')

@@

```{r hs-print-both, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_both.RDS') %>% head(n=20)

@@

```{r hs-table-both-agg, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_agg_both.RDS')

@@

<!-- FIGURES -->

@@

@@

```{r privhs-universe, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of universe of private HS and private HS that received at least 1 visit from sample institutions, unweighted and weighted by 12th grade enrollment"}
knitr::include_graphics('./../assets/figures/plot_pss_universe.pdf')
```

\begin{center}
* \textit{Universe of private HS (N=3673), private HS visited by sample institutions (N=1738); Universe of private HS is defined as any private schools that enrolls at least ten grade 12 students and is not a special education school, an alternative school, an early childhood center, or an independent school.}
\end{center}

@@

```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by private institutions"}
knitr::include_graphics('./../assets/figures/ego_network_figure_privu.pdf')
```

>>>>

Table \@ref(fig:event-count-figure-pubu): event count public universities

Table \@ref(fig:event-count-figure-privu): event count, private univerisites

@@

```{r, include = FALSE}
# ggplot's default color palette
 library(scales)
# show_col(hue_pal()(4))

@@

  c <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privc', '.RDS'))),
    'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE
  )

  grid.arrange(a, b, c, nrow=3, ncol=1)

@@

@@

```{r hs-print-privu, echo = FALSE, eval = FALSE}
df <- readRDS('./../assets/tables/table_2mode_privu.RDS') %>% head(n=20)

@@

```{r hs-table-privu-agg, echo = FALSE, eval = FALSE}
df <- readRDS('./../assets/tables/table_2mode_agg_privu.RDS')

@@

```{r hs-print-pubu, echo = FALSE, eval = FALSE}
df <- readRDS('./../assets/tables/table_2mode_pubu.RDS') %>% head(n=20)

@@

```{r hs-table-pubu-agg, echo = FALSE, eval = FALSE}
df <- readRDS('./../assets/tables/table_2mode_agg_pubu.RDS')

@@

```{r hs-print-both, echo = FALSE, eval = FALSE}
df <- readRDS('./../assets/tables/table_2mode_both.RDS') %>% head(n=20)

@@

```{r hs-table-both-agg, echo = FALSE, eval = FALSE}
df <- readRDS('./../assets/tables/table_2mode_agg_both.RDS')

@@

<!-- ###################################################################################### FIGURES -->

@@

<!-- ########################################################## RQ 1: SCALE -->

```{r event-count-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for public institutions"}
knitr::include_graphics('./../assets/figures/plot_event_count_pubu.pdf')
```

```{r event-count-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for private institutions"}
knitr::include_graphics('./../assets/figures/plot_event_count_privu.pdf')
```

<!-- ADD FIGURES: FIGURE X. Number of events at public high schools and private high schools 
      within each university, separate line for in-state and out-of-state
      separate figures for public and private universities
-->

<!-- ADD FIGURES: FIGURE X. Actual vs. proportional number of visits to private high schools
      within each university, separate line for in-state and out-of-state
      separate figures for public and private universities
-->

<!-- ########################################################## RQ 2: Characteristics of high schools -->

@@

```{r ego-network-figure-region, fig.align = 'center', echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_region.pdf')
```

```{r ego-network-figure-religion, fig.align = 'center', echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_religion.pdf')
```

```{r ego-network-figure-hs-rank, fig.align = 'center', echo = FALSE, fig.cap = "Academic reputation of of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank.pdf')
```

```{r ego-network-figure-race, fig.align = 'center', echo = FALSE, fig.cap = "Racial composition of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_race.pdf')
```

```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, eval=FALSE, fig.cap = "Characteristics of private HS visited by private institutions"}
knitr::include_graphics('./../assets/figures/ego_network_figure_privu.pdf')
```

```{r privhs-universe, fig.align = 'center', echo = FALSE, eval = FALSE,fig.cap = "Characteristics of universe of private HS and private HS that received at least 1 visit from sample institutions, unweighted and weighted by 12th grade enrollment"}
knitr::include_graphics('./../assets/figures/plot_pss_universe.pdf')
```

<!-- 
\begin{center}
* \textit{Universe of private HS (N=3673), private HS visited by sample institutions (N=1738); Universe of private HS is defined as any private schools that enrolls at least ten grade 12 students and is not a special education school, an alternative school, an early childhood center, or an independent school.}
\end{center}
-->

<!-- RQ3: Overlapping sets of high schools -->

@@
